Plots for Latent Hawkes Paper

### 2020-11-16 output_scripts/Paper_Plots.Rmd
update these sims to do fig 4 for data from both m1 and m2

library(rstan)
Sys.setenv(LOCAL_CPPFLAGS = '-march=corei7 -mtune=corei7')
options(mc.cores = parallel::detectCores())
library(tidyverse)
library(R.utils)
library(RColorBrewer)
library(fields)
library(bayesplot)
library(viridis)
library(compete)
library(colorspace)
source(paste(func_dir,'naiveRankHierarchy.R',sep = ""))
source(paste(func_dir,'expertRankHierarchy.R',sep = ""))
source(paste(func_dir,'cleanData.R',sep = "")) 
source(paste(func_dir,'prepareDataStan.R',sep = "")) 
source(paste(func_dir,'inferLatentMmhp.R',sep = ""))
source(paste(func_dir,'plotUtil.R',sep = "")) 
source(paste(func_dir,'mmhp.R',sep = ""))
source(paste(func_dir,'uniHawkes.R',sep = ""))
source(paste(func_dir,'simulatePrediction.R',sep = ""))
source(paste(func_dir,'myGlicko.R',sep = ""))
source(paste(func_dir,'matrixPlotParameter.R',sep = ""))
source(paste(func_dir,'residualStructureScore.R',sep = ""))
source(paste(func_dir,'drawIntensity.R',sep =""))
source("https://gist.githubusercontent.com/jalapic/6ca3ece44bdcdc522bb735f183aa0ca0/raw/1a07f469eff08117121b6cbebcd22fb7569e3ee8/compete_extra.R")

@@

### need to load in the interpolated latent state here
#### TO DO ####

@@

lambda.true <- mmhpTrueIntensityNumeric(params=object_true,
                                        t=temp.t,
                       latent=list(x=fixStateTransition(test.mmhp)$x,
                              z=fixStateTransition(test.mmhp)$z),
                              time.vec=time.segment)
```

>>>>

library(here)
library(rstan)
Sys.setenv(LOCAL_CPPFLAGS = '-march=corei7 -mtune=corei7')
options(mc.cores = parallel::detectCores())
library(tidyverse)
library(R.utils)
library(RColorBrewer)
library(fields)
library(bayesplot)
library(viridis)
library(compete)
library(colorspace)
source(paste(func_dir,'naiveRankHierarchy.R',sep = ""))
source(paste(func_dir,'expertRankHierarchy.R',sep = ""))
source(paste(func_dir,'cleanData.R',sep = "")) 
source(paste(func_dir,'prepareDataStan.R',sep = "")) 
source(paste(func_dir,'inferLatentMmhp.R',sep = ""))
source(paste(func_dir,'plotUtil.R',sep = "")) 
source(paste(func_dir,'mmhp.R',sep = ""))
source(paste(func_dir,'uniHawkes.R',sep = ""))
source(paste(func_dir,'simulatePrediction.R',sep = ""))
source(paste(func_dir,'myGlicko.R',sep = ""))
source(paste(func_dir,'matrixPlotParameter.R',sep = ""))
source(paste(func_dir,'residualStructureScore.R',sep = ""))
source(paste(func_dir,'drawIntensity.R',sep =""))
source("https://gist.githubusercontent.com/jalapic/6ca3ece44bdcdc522bb735f183aa0ca0/raw/1a07f469eff08117121b6cbebcd22fb7569e3ee8/compete_extra.R")

@@

state_est_fits <- list.files(m1_path, pattern = "fit123_state_est_M1*")
load(paste0(m1_path,state_est_fits[plot.s]))

state.est.latent.mmhp <- interpolate_state_est_lst[plot.i,plot.j][[1]]
state.est.latent.mmhp.new <- fixInterpolateState(state.est.latent.mmhp,
                                                 termination=200)

@@

lambda.m3 <- mmhpIntensityNumeric(params=object_hat,
                                  t=temp.t,
                                  time.vec=time.segment,
                                  latent.vec=step.fun.est(time.segment))

object_true <- lapply(object_matrix,function(x) x[plot.i,plot.j])
names(object_true) <- c("lambda0","lambda1","alpha","beta")

lambda.true <- uniHawkesIntensityNumeric(object = object_true,
                                        events =temp.t,
                                        time.vec = time.segment)
```

```{r fig 4b M1 sim}
source(here("lib","mod_drawHawkesIntensityPaper.R"))
y.ub <- c(17,17,17)#c(130,72,31)
x_events <- 135#150
#model_colors <- c("steelblue", "goldenrod2", "firebrick2")
model_colors <- viridis::viridis(3)
layout(matrix(c(1:6), 6, 1), heights=rep(c(2.5,1),3))
layout(matrix(c(1:6), 6, 1), heights=rep(c(7.5,1),3))
my.xlim <- 140#160#200#130
my.long.x <- 140#205#134.5
legend.x <- c(50,50,50)#c(135,135,135)
legend.y <- #c(34,32,32)
legend.y <- c(15,12,15)#c(62,37,18)#c(22,22,22)
legend.cex <- 1.5 #3
line.alpha <- c(0.9,0.6)
line.wdth <- c(2,2.5)
negative.col <- add.alpha('lightskyblue',0.6)
positive.col <- add.alpha('tomato',0.6)
#negative.col <- viridis::viridis(5,alpha = 0.6)[1]
#positive.col <- viridis::viridis(5,alpha = 0.6)[4]
par(mar = c(0,0.3,0,0.1), oma = c(3,3.5,4,0),
    tcl=0.2,mgp=c(0.5,0,0), xpd=TRUE)

# model1
############
true.object <- object_true
# lambda.true$lambda.t <- lambda.est
# lambda.true$time.vec <- lambda.m1$time.vec

mod_drawHawkesIntensityPaper(lambda0 = true.object$lambda0,
                             alpha = true.object$alpha,
                             beta = true.object$beta,
                             events = temp.t,
                             add = FALSE,
                            yupper=y.ub[1],
                            color=add.alpha("black", alpha=line.alpha[1]),
                            line.width=line.wdth[1],
                            y.ratio=-0.05, min.y=-2, min.x=0, max.x=my.xlim,
                            title_name=paste(plot.i,"->",plot.j),
                            title.cex = 2,
                            box.type="n")
drawHawkesIntensityPaper(lambda0=model1_par_est$lambda0,
                         alpha=model1_fn$alpha.fun(model1_par_est$f[plot.i],
                                                   model1_par_est$f[plot.j],
                                                   model1_par_est$eta_1,
                                                   model1_par_est$eta_2,
                                                   model1_par_est$eta_3),
                         beta=model1_par_est$beta,
                         events=temp.t,
                         color=add.alpha(model_colors[1],
                                         alpha=line.alpha[2]),
                         line.width=line.wdth[2])

legend(legend.x[1],legend.y[1],c("True"),
       col = c("black"),
       y.intersp=0.88,x.intersp=0.15,bty = "n",
       lty = c(1), lwd = c(5), cex=legend.cex,seg.len=1)
legend(legend.x[1]+18,legend.y[1],c("C-HP"),
       col = c(model_colors[1]),
       y.intersp=0.88,x.intersp=0.15,bty = "n",
       lty = c(1), lwd = c(5), cex=legend.cex,seg.len=1)

# model2
############
mod_drawHawkesIntensityPaper(lambda0 = true.object$lambda0,
                             alpha = true.object$alpha,
                             beta = true.object$beta,
                             events = temp.t,
                             add = FALSE,
                            yupper=y.ub[1],
                            color=add.alpha("black", alpha=line.alpha[1]),
                            line.width=line.wdth[1],
                            y.ratio=-0.05, min.y=-2, min.x=0, max.x=my.xlim,
                            title_name=paste(plot.i,"->",plot.j),
                            title.cex = 2,
                            box.type="n")
drawHawkesIntensityPaper(lambda0=model2_par_est$gamma[plot.i]+
                           model2_par_est$zeta[plot.j],
                         alpha=model1_fn$alpha.fun(model2_par_est$f[plot.i],
                                                   model2_par_est$f[plot.j],
                                                   model2_par_est$eta_1,
                                                   model2_par_est$eta_2,
                                                   model2_par_est$eta_3),
                         beta=model2_par_est$beta,
                         events=temp.t,
                         color=add.alpha(model_colors[2],
                                         alpha=line.alpha[2]),
                         line.width=line.wdth[2])
legend(legend.x[2],legend.y[2],"C-DCHP",
       col = model_colors[2],
       y.intersp=0.88,x.intersp=0.1,bty = "n",
       lty = 1, lwd = 5, cex= legend.cex,seg.len=1)

# model3
########
par(mar = c(0,0.3,1,0.1))
mod_drawHawkesIntensityPaper(lambda0 = true.object$lambda0,
                             alpha = true.object$alpha,
                             beta = true.object$beta,
                             events = temp.t,
                             add = FALSE,
                            yupper=y.ub[1],
                            color=add.alpha("black", alpha=line.alpha[1]),
                            line.width=line.wdth[1],
                            y.ratio=-0.05, min.y=-2, min.x=0, max.x=my.xlim,
                            title_name=paste(plot.i,"->",plot.j),
                            title.cex = 2,
                            box.type="n")
drawUniMMHPIntensityPaper(object_hat,
                          simulation = list(
  x=state.est.latent.mmhp.new$x.hat,                                          
  z=state.est.latent.mmhp.new$z.hat,
  tau=temp.t,
  lambda.max=max(lambda.m3)),
                          yupper=y.ub,add=TRUE,
                          color=add.alpha(model_colors[3],
                                      alpha=line.alpha[2]),
  line.width=line.wdth[2])
legend(legend.x[3],legend.y[3],"C-MMHP",
       col = model_colors[3],
       y.intersp=0.88,x.intersp=0.1,bty = "n",
       lty =1, lwd = 5,cex=legend.cex,seg.len=1)
## draw box
axis(1,at=c(-2,my.long.x),col="gray35",
     line=0.5,tick=T,labels=rep("",2),lwd=0.5,lwd.ticks=0,lty=3)

## top
mtext(text="M1 Sim",side=3,line=0.8,outer=TRUE,cex=2.5,font=2)
## bottom
mtext(text="Time",side=1,line=2,outer=TRUE,cex=2.5)
## left
mtext(text="Intensity",side=2,line=0.6,outer=TRUE,cex=2.5)

```{r process m2 for fig4b}
plot.s <- 1#7#9
plot.i <- 4
plot.j <- 5

load(paste0(m2_path,m2_files[plot.s]))

temp.t <- sim_model2_data[[1]]$day_hour[ which(sim_model2_data[[1]]$start == cur_i & 
                  sim_model2_data[[1]]$end == cur_j)]
# temp.t <- test.mmhp$tau
current.n <- length(temp.t)-1
time.segment <- seq(0,tail(temp.t,1),length.out=5000)

### Preprocess the model inference result
## model 1
#########
model1_par_est <- list(lambda0 =
                         mean(sim_model2_stan_sim1_total[[plot.s]]$lambda0[1001:2000]),
                       eta_1=mean(sim_model2_stan_sim1_total[[plot.s]]$eta_1[1001:2000]),
                       eta_2=mean(sim_model2_stan_sim1_total[[plot.s]]$eta_2[1001:2000]),
                       eta_3=mean(sim_model2_stan_sim1_total[[plot.s]]$eta_3[1001:2000]),
                       beta=mean(sim_model2_stan_sim1_total[[plot.s]]$beta[1001:2000]),
                       f=apply(sim_model2_stan_sim1_total[[plot.s]]$f[1001:2000,],2,mean))
lambda.m1<-uniHawkesIntensityNumeric(object=list(lambda0 = 
                                                   model1_par_est$lambda0,
                                    alpha =
                                      model1_fn$alpha.fun(model1_par_est$f[plot.i],
                                    model1_par_est$f[plot.j],
                                    model1_par_est$eta_1,
                                    model1_par_est$eta_2,
                                    model1_par_est$eta_3),
                                    beta=model1_par_est$beta),
                                     events=temp.t,
                                     time.vec=time.segment)

## model2
#############
model2_par_est <- list(gamma=apply(sim_model2_stan_sim2_total[[plot.s]]$gamma[1001:2000,],
                                   2,mean),
                    zeta = 
                      apply(sim_model2_stan_sim2_total[[plot.s]]$zeta[1001:2000,],2,mean),
                       eta_1=mean(sim_model2_stan_sim2_total[[plot.s]]$eta_1[1001:2000]),
                       eta_2=mean(sim_model2_stan_sim2_total[[plot.s]]$eta_2[1001:2000]),
                       eta_3=mean(sim_model2_stan_sim2_total[[plot.s]]$eta_3[1001:2000]),
                       beta=mean(sim_model2_stan_sim2_total[[plot.s]]$beta[1001:2000]),
                       f=apply(sim_model2_stan_sim2_total[[plot.s]]$f[1001:2000,],2,mean))

## Model3
#############
mmhp_par_est <- list(lambda0=mean(sim_model2_stan_sim3_total[[plot.s]]$lambda0[1001:2000]),
                     lambda1=mean(sim_model2_stan_sim3_total[[plot.s]]$lambda1[1001:2000]),
                     eta_1=mean(sim_model2_stan_sim3_total[[plot.s]]$eta_1[1001:2000]),
                     eta_2=mean(sim_model2_stan_sim3_total[[plot.s]]$eta_2[1001:2000]),
                     eta_3=mean(sim_model2_stan_sim3_total[[plot.s]]$eta_3[1001:2000]),
                     beta=mean(sim_model2_stan_sim3_total[[plot.s]]$beta[1001:2000]),
                     f=apply(sim_model2_stan_sim3_total[[plot.s]]$f[1001:2000,],2,mean))

state_est_fits <- list.files(m2_path, pattern = "fit123_state_est_M2*")
load(paste0(m2_path,state_est_fits[plot.s]))

state.est.latent.mmhp <- interpolate_state_est_lst[plot.i,plot.j][[1]]
state.est.latent.mmhp.new <- fixInterpolateState(state.est.latent.mmhp,
                                                 termination=200)

lambda.m3 <- mmhpIntensityNumeric(params=object_hat,
                                  t=temp.t,
                                  time.vec=time.segment,
                                  latent.vec=step.fun.est(time.segment))

object_true <- lapply(object_matrix,function(x) x[plot.i,plot.j])
names(object_true) <- c("lambda0","lambda1","alpha","beta")

lambda.true <- uniHawkesIntensityNumeric(object = object_true,
                                        events =temp.t,
                                        time.vec = time.segment)
```

```{r fig 4b M2 sim}
source(here("lib","mod_drawHawkesIntensityPaper.R"))
y.ub <- c(17,17,17)#c(130,72,31)
x_events <- 135#150
#model_colors <- c("steelblue", "goldenrod2", "firebrick2")
model_colors <- viridis::viridis(3)
layout(matrix(c(1:6), 6, 1), heights=rep(c(2.5,1),3))
layout(matrix(c(1:6), 6, 1), heights=rep(c(7.5,1),3))
my.xlim <- 140#160#200#130
my.long.x <- 140#205#134.5
legend.x <- c(50,50,50)#c(135,135,135)
legend.y <- #c(34,32,32)
legend.y <- c(15,12,15)#c(62,37,18)#c(22,22,22)
legend.cex <- 1.5 #3
line.alpha <- c(0.9,0.6)
line.wdth <- c(2,2.5)
negative.col <- add.alpha('lightskyblue',0.6)
positive.col <- add.alpha('tomato',0.6)
#negative.col <- viridis::viridis(5,alpha = 0.6)[1]
#positive.col <- viridis::viridis(5,alpha = 0.6)[4]
par(mar = c(0,0.3,0,0.1), oma = c(3,3.5,4,0),
    tcl=0.2,mgp=c(0.5,0,0), xpd=TRUE)

# model1
############
true.object <- object_true
# lambda.true$lambda.t <- lambda.est
# lambda.true$time.vec <- lambda.m1$time.vec

mod_drawHawkesIntensityPaper(lambda0 = true.object$lambda0,
                             alpha = true.object$alpha,
                             beta = true.object$beta,
                             events = temp.t,
                             add = FALSE,
                            yupper=y.ub[1],
                            color=add.alpha("black", alpha=line.alpha[1]),
                            line.width=line.wdth[1],
                            y.ratio=-0.05, min.y=-2, min.x=0, max.x=my.xlim,
                            title_name=paste(plot.i,"->",plot.j),
                            title.cex = 2,
                            box.type="n")
drawHawkesIntensityPaper(lambda0=model1_par_est$lambda0,
                         alpha=model1_fn$alpha.fun(model1_par_est$f[plot.i],
                                                   model1_par_est$f[plot.j],
                                                   model1_par_est$eta_1,
                                                   model1_par_est$eta_2,
                                                   model1_par_est$eta_3),
                         beta=model1_par_est$beta,
                         events=temp.t,
                         color=add.alpha(model_colors[1],
                                         alpha=line.alpha[2]),
                         line.width=line.wdth[2])

legend(legend.x[1],legend.y[1],c("True"),
       col = c("black"),
       y.intersp=0.88,x.intersp=0.15,bty = "n",
       lty = c(1), lwd = c(5), cex=legend.cex,seg.len=1)
legend(legend.x[1]+18,legend.y[1],c("C-HP"),
       col = c(model_colors[1]),
       y.intersp=0.88,x.intersp=0.15,bty = "n",
       lty = c(1), lwd = c(5), cex=legend.cex,seg.len=1)

# model2
############
mod_drawHawkesIntensityPaper(lambda0 = true.object$lambda0,
                             alpha = true.object$alpha,
                             beta = true.object$beta,
                             events = temp.t,
                             add = FALSE,
                            yupper=y.ub[1],
                            color=add.alpha("black", alpha=line.alpha[1]),
                            line.width=line.wdth[1],
                            y.ratio=-0.05, min.y=-2, min.x=0, max.x=my.xlim,
                            title_name=paste(plot.i,"->",plot.j),
                            title.cex = 2,
                            box.type="n")
drawHawkesIntensityPaper(lambda0=model2_par_est$gamma[plot.i]+
                           model2_par_est$zeta[plot.j],
                         alpha=model1_fn$alpha.fun(model2_par_est$f[plot.i],
                                                   model2_par_est$f[plot.j],
                                                   model2_par_est$eta_1,
                                                   model2_par_est$eta_2,
                                                   model2_par_est$eta_3),
                         beta=model2_par_est$beta,
                         events=temp.t,
                         color=add.alpha(model_colors[2],
                                         alpha=line.alpha[2]),
                         line.width=line.wdth[2])
legend(legend.x[2],legend.y[2],"C-DCHP",
       col = model_colors[2],
       y.intersp=0.88,x.intersp=0.1,bty = "n",
       lty = 1, lwd = 5, cex= legend.cex,seg.len=1)

# model3
########
par(mar = c(0,0.3,1,0.1))
mod_drawHawkesIntensityPaper(lambda0 = true.object$lambda0,
                             alpha = true.object$alpha,
                             beta = true.object$beta,
                             events = temp.t,
                             add = FALSE,
                            yupper=y.ub[1],
                            color=add.alpha("black", alpha=line.alpha[1]),
                            line.width=line.wdth[1],
                            y.ratio=-0.05, min.y=-2, min.x=0, max.x=my.xlim,
                            title_name=paste(plot.i,"->",plot.j),
                            title.cex = 2,
                            box.type="n")
drawUniMMHPIntensityPaper(object_hat,
                          simulation = list(
  x=state.est.latent.mmhp.new$x.hat,                                          
  z=state.est.latent.mmhp.new$z.hat,
  tau=temp.t,
  lambda.max=max(lambda.m3)),
                          yupper=y.ub,add=TRUE,
                          color=add.alpha(model_colors[3],
                                      alpha=line.alpha[2]),
  line.width=line.wdth[2])
legend(legend.x[3],legend.y[3],"C-MMHP",
       col = model_colors[3],
       y.intersp=0.88,x.intersp=0.1,bty = "n",
       lty =1, lwd = 5,cex=legend.cex,seg.len=1)
## draw box
axis(1,at=c(-2,my.long.x),col="gray35",
     line=0.5,tick=T,labels=rep("",2),lwd=0.5,lwd.ticks=0,lty=3)

## top
mtext(text="M2 Sim",side=3,line=0.8,outer=TRUE,cex=2.5,font=2)
## bottom
mtext(text="Time",side=1,line=2,outer=TRUE,cex=2.5)
## left
mtext(text="Intensity",side=2,line=0.6,outer=TRUE,cex=2.5)
